Guarded Recursion in Agda via Sized Types

### 2019-01-29 code-oneclock-paper/latex/paper.tex
rewrote 5.1 minorly

\section{Modelling Guarded Recursion}
\label{sec:guarded}
In this section we add the guarded
recursive and coinductive features to the denotational semantics.
%Now we have the simple type formers and their terms.
%The next step is to add the type formers required for guarded recursion.
We start by defining the semantic box modality together with its
introduction and elimination rule. Then we construct the semantic
later modality. We show how to define the fixpoint combinator and the
force operation using sized types. In the end we discuss how to model
guarded recursive types.
%% introduce the
%% semantic 
%%  together with the
%% terms associated 
%% and how to construct terms of those types.
%% With this in place, we define the fixpoint combinator.
%% In the end, we give the type former for guarded recursive types.

>>>>

\section{Modelling Guarded Recursion}
\label{sec:guarded}
In this section, we add the required guarded
recursive and coinductive features to the denotational semantics.
%Now we have the simple type formers and their terms.
%The next step is to add the type formers required for guarded recursion.
We start by defining the semantic box modality together with its
introduction and elimination rule. Then we construct the semantic
later modality. We show how to define the fixpoint combinator and the
force operation using sized types. In the end, we discuss how to model
guarded recursive types.
%% introduce the
%% semantic 
%%  together with the
%% terms associated 
%% and how to construct terms of those types.
%% With this in place, we define the fixpoint combinator.
%% In the end, we give the type former for guarded recursive types.
